---
output: rmarkdown::github_document
---

# pressur

Query and Orchestrate the 'WordPress' 'API'

## Description

'WordPress' has a fairly comprehensive 'API' <https://developer.wordpress.com/>
that makes it possible to perform blog orchestration ('CRUD' operations on posts, users,
sites, etc.) as well as retrieve and process blog statistics. Tools are provided to work
with the 'WordPress' 'API' functions.

### `<dalek_voice>` YOU WILL O-BEY `</dalek_voice>`

WordPress API requiring authentication means you have to do the OAuth2 dance, and most API calls require authentication. That means you need to start off working with the WordPress API in/from `pressur` using the `wp_auth()` function. For that to work, **YOU MUST**::

=> Go here and make an app: <https://developer.wordpress.com/apps/>  

=> Put the `Client ID` you receive into `~/.Renviron` with a line that looks like:

    `WORDPRESS_API_KEY=#####`
    
=> Put the `Client Secret` you receive into `~/.Renviron` with a line that looks like:

    `WORDPRESS_API_SECRET=Yn50ds........`

And start with a fresh R session for any of this to even have a remote possibility of working.

I'll make friendlier documentation for ^^ in the near future.

### NOTE

Only minimal functionality is provided at present (enough to get stats out).

You are encouraged to poke around the source and contribute PRs or issues for high priority items you'd like to see in the package.

## What's Inside The Tin

The following functions are implemented:

- `wp_auth`:	Authenticate to WordPress
- `wp_about_me`:	Get your user information
- `wp_get_my_posts`:	Get all 'my' posts across all sites
- `wp_post_stats`:	Retrieve statistics for a WordPress post
- `wp_site_info`:	Get information about a site
- `wp_site_stats`:	Get a site's stats

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/pressur")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(pressur)

# current verison
packageVersion("pressur")
```

### Basic operation

```{r}
wp_auth()
me <- wp_about_me()
dplyr::glimpse(wp_site_stats(me$primary_blog))
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

